---
title       : Developing Data Products Project Pitch
subtitle    : ROAS App
author      : Jean Rafael Angeles
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]  # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## __Overview__

### _Google Analytics_ is a useful tool that provides you insights for your website. There are two versions currently available. The free standard __Google Analytics(GA)__ and the subscription based __Google Analytics Premium(GAP)__.

--- .class #id 

## __The Problem__

### Sadly GAP is a costly product. It's suited for sites with large traffic. GAP also has analytics features not present in GA. One of such is the _ROI Analysis Tool_.

--- 

## __Here's An Alternative__

### The _ROAS app_ is basically an indepented ROI Analysis Tool. It enables standard GA users to experience the ROI Analysis Tool without the need for GAP subscription.

---

## __Prior Data Cleaning__

Here's a sample of the state the data coming from GA looks like:

```{r, echo=FALSE}
MCF.Channel.Grouping <- c('Paid Search','Display','Organic Search','Direct','Referral','(Other)','Email','Social Network','')
Spend <- c('A$215,093.54','A$55,561.20','A$16,000.68','â???"','â???"','â???"','â???"','â???"','â???')
Conversions <- c('401','335','1,000','1,111','105','8','55','5','3,020')
Conversion.Value <- c('A$169,511.05','A$16,025.66','A$15,709.03','A$1,208,675.71','A$911,730.32','A$69,483.56','A$41,000.08','A$8,160.89','A$3,415,767.3')
data <- data.frame(MCF.Channel.Grouping,Spend,Conversions,Conversion.Value,stringsAsFactors = FALSE)
head(data)
```

The raw data isn't readily available for the needed computation so data cleaning codes.

---

## __After Data Cleaning__

Here's what the data looks like after cleaning it.

```{r, echo=FALSE, warning=FALSE}
    data <- data[which(data$MCF.Channel.Grouping!=""),]
    data$Spend <- gsub("A\\$|,","",data$Spend)
    data$Spend <- as.numeric(data$Spend)
    data$Spend[is.na(data$Spend)] <- 0
    data$Conversions <- gsub("A|\\$|,","",data$Conversions)
    data$Conversions <- as.numeric(data$Conversions)
    data$Conversions[is.na(data$Conversions)] <- 0
    data$Conversion.Value <- gsub("A|\\$|,","",data$Conversion.Value)
    data$Conversion.Value <- as.numeric(data$Conversion.Value)
    data$Conversion.Value[is.na(data$Conversion.Value)] <- 0
    data$ROAS <- data$Conversion.Value/data$Spend
    head(data)
```

---

## __Computations__

Here's the computations that has been formatted as well.

__Spend__
```{r, echo=FALSE}
spend_sum <- sum(data$Spend)
spend_sum_display <- prettyNum(spend_sum, big.mark=",",preserve.width="none")
spend_sum_display <- paste0("$",spend_sum_display)
spend_sum_display

```

__Conversions__
```{r, echo=FALSE}
conversions_sum <- sum(data$Conversions)
conversions_sum_display <- prettyNum(conversions_sum, big.mark=",",preserve.width="none")
conversions_sum_display
```

__Conversion Value__
```{r, echo=FALSE}
conversion.value_sum <- sum(data$Conversion.Value)
conversion.value_sum_display <- prettyNum(conversion.value_sum, big.mark=",",preserve.width="none")
conversion.value_sum_display <- paste0("$",conversion.value_sum_display)
conversion.value_sum_display
```

__ROAS__
```{r, echo=FALSE}
roas_sum <- conversion.value_sum/spend_sum
roas_sum <- sprintf("%1.2f%%", roas_sum)
roas_sum <- prettyNum(roas_sum, big.mark=",",preserve.width="none")
roas_sum
```
